The impact of gas bulk rotation on the Lyman-$\alpha$ line

### 2013-11-01 paper/ms.tex
edits in the off-center section

\begin{figure*}
  \includegraphics[width=0.45\textwidth]{SpectraDifVelocitiesCentral.png}
  \includegraphics[width=0.45\textwidth]{SpectraDifVelocitiesHOM.png}
\caption{Shape of the \ly line for
    different velocities rotational velocities for spherical
    distributions with $\tau_{H}=10^{7}$. The left (right) panel shows
    the central (homogeneous) photon distribution. All photons were
    taken into  account regardless of their final direction of propagation.
    \label{fig:differentvelocities}}  
\end{figure*}

@@

\begin{figure}
  \includegraphics[scale=0.3]{OF_spheres.png}
  \caption{The two solid circles show the two different spherical off-centred emitting
    regions. The angular velocity vector is defined to be along the
    $\hat{\i}$ direction and the observer is along the $\hat{\j}$ direction (where
    the reader is). 
    \label{fig:OCspheres}} 
\end{figure}

The model with homogeneous radiation sources allows to study the
effect of radiation sources distributed with a different symmetry than
the gas. We select photons emitted in spheres that are off-centred
with respect to the gas distribution.

@@

We study first the deviations of the received flux on the surface of the
sphere. We follow \cite{Zheng2013} to estimate the flux seen by an
observer located at an angle $\Theta$ (distant observer angle)
normalized to the isotropic flux:

\begin{equation}
F(\mu) = \frac{2\Delta N}{N\Delta \mu}, 
\end{equation}
%
Where $\mu=\cos\Theta$, $N$ is the total number of outgoing photons,
$\Delta N$ is the number of photons in a angular bin $\Delta
\Theta$. This definition satisfies the condition
$\int_{-1}^{1}F(\mu)d\mu/2=1$.

For the central and homogeneous source distributions we find that the
level of isotropy angular dependency represented by $\mu$ doesn't show
a considerable variation in particular the observer would infer
luminosities  different from the isotropical value only at levels $<
3\%$. This values were obtained for a run with $V_{\rm max}=(50kms^{-1}, 
100kms^{-1}, 200kms^{-1}, 300kms^{-1})$ and $\tau_{\rm H}=10^{5}, 10^{6}, 
10^{7}$ and $N_{\gamma}=10^{5}$ photons.

For the Off-center emission Fig.\ref{fig:OCflux} the variations of 
$\mu$ increase as the rotational velocity increase, for $V_{\rm max}=(50kms^{-1}$
 $\bigtriangleup\mu \leq 7\%$ , for $V_{\rm max}=(100kms^{-1}$
$\bigtriangleup\mu\leq 12\%$ and finally for $V_{\rm max}=(200kms^{-1}$
$\bigtriangleup\mu\leq 15\%$. This would imply that the amount of flux
we measure would depend in the angle between our line of sight and 
the rotation axis of the galaxy. 
%%%%%%%

The outgoing spectra for two different spheres located at $\pm 0.5R$ 
are shown in Fig.\ref{fig:OC_profiles}, we have shown this positions because
the resulting profiles show new interesting morphologies than are not
found in the $\pm 0.25R$ case.

\begin{figure}
\includegraphics[scale=0.3]{mu_OC.png}
\caption{Flux angular dependency for Off-center distribution, different line widths illustrate different
off-center positions.
   \label{fig:OCflux}} 
\end{figure}

The main effect we found in the off-center emission is that for 
some models ($\tau = 10^6, V=100 km s^{-1}$ and $\tau = 10^7, V=200 km s^{-1}$)
the line presents three peaks (blue-shifted, centred, red-shifted),
to obtain clearest profiles concerning this results we run three models 
with $\tau_{\gamma}=10^{6}$, This profiles are shown in 
Fig.\ref{fig:OC_profiles_N6}, where we clearly observe the presence of 
three peaks, and also we do not find any asymmetry in the line 
produced by the off-center emission.

For models with ($[\tau = 10^{5}, V=100 km s^{-1}]$ ,
$[\tau = 10^6, V=200 km s^{-1}]$ and $ [\tau = 10^{7}, 
V=300 km s^{-1}]$) the centred line is dominant but the presence of
the redder and bluer peak in also present which is also a new result.
Also as in the homogeneous / central model the line is broader at high 
rotational velocities.

\begin{figure*}
\includegraphics[scale=0.3]{OC_profiles.png}
\caption{$\mathrm{Ly}\alpha$ profiles for the off-center positions.
dashed lines represents spheres locate at $-0,5R$ while solid lines 
represents spheres at $0.5R$)
   \label{fig:OC_profiles}} 
\end{figure*}

\begin{figure*}
\includegraphics[scale=0.3]{NewPanel_N6_atpm5.png}
\caption{$\mathrm{Ly}\alpha$ profiles for the off-center positions.
green lines represents spheres locate at $-0,5R$ while red lines 
represents spheres at $0.5R$)
   \label{fig:OC_profiles_N6}} 
\end{figure*}

>>>>

\begin{figure*}
\begin{center}
  \includegraphics[width=0.45\textwidth]{SpectraDifVelocitiesCentral.png}
  \includegraphics[width=0.45\textwidth]{SpectraDifVelocitiesHOM.png}
\end{center}
\caption{Shape of the \ly line for
    different velocities rotational velocities for spherical
    distributions with $\tau_{H}=10^{7}$. The left (right) panel shows
    the central (homogeneous) photon distribution. All photons were
    taken into  account regardless of their final direction of propagation.
    \label{fig:differentvelocities}}  
\end{figure*}

@@

\begin{figure}
  \includegraphics[scale=0.35]{OF_spheres.png}
  \caption{The two solid circles show the two different spherical
    off-centred emitting  regions. The angular velocity vector is
    defined to be along the $\hat{\i}$ direction and the observer is
    along the $\hat{\j}$ direction (where the reader is). 
    \label{fig:OCspheres}} 
\end{figure}

The model with homogeneous radiation sources allows to study the
effect of radiation sources distributed with a different symmetry than
the gas. We select photons emitted in off-centred spheres 
with respect to the gas distribution.

@@

We study first the angular deviations of the outgoing photons with respect
to an isotropic flux. We follow \cite{Zheng2013} to estimate the flux
as a function of the angle $\Theta$ formed by the outgoing photons and
a fixed direction (the $\vec{k}$ direction in this case). This is
expressed by

\begin{equation}
F(\mu) = \frac{2\Delta N}{N\Delta \mu}, 
\end{equation}
%
where $\mu=\cos\Theta$, $N$ is the total number of outgoing photons,
$\Delta N$ is the number of photons in a angular bin $\Delta
\Theta$. This definition satisfies the condition
$\int_{-1}^{1}F(\mu)d\mu/2=1$.

In the the off-center emission the variations  in the $\mu$ distribution
$\mu$ increase with the rotational velocity. For $V_{\rm max}= 50$\kms
 $\Delta \mu \leq 7\%$; $V_{\rm max}=100$\kms, $\Delta \mu\leq 12\%$
and $V_{\rm max}=200$\kms, $\Delta\mu\leq 15\%$ (NOTE: regardless of
$\tau$??). This implies a strong dependence of the observed flux on
the relative position of an observer.  In contrast,the central and
homogeneous source distributions only show a weak anisotropy at the level of
$\Delta\mu\leq 3\%$.

Figure \ref{fig:OC_profiles} show the spectra for the two off-centered
spheres located at $C=\pm0.5R$.  The most interesting effect is that
emission is that in  some models ($\tau = 10^6, V=100,200$\kms and $\tau =
10^7, V=200,300$\kms) the line presents three peaks (blue-shifted,
centred, red-shifted). However, we do not find any asymmetry in the line 
produced by the off-center emission. As in the homogeneous / central
model the line gets broader as the rotational velocity increases.

The results for the off-centered spheres placed closed to the center
at $C=\pm 0.25R$ do not display the features discussed above for the
spheres at $C=\pm0.5R$.

\begin{figure}
\includegraphics[scale=0.35]{mu_OC.png} \caption{Flux angular 
  dependency for off-center distribution. Different line widths
  illustrate different rotational velocities.\label{fig:OCflux}} 
\end{figure}

\begin{figure*}
\includegraphics[scale=0.3]{OC_profiles.png}
\caption{\ly profiles for the off-center positions. Dashed/solide
  lines represents spheres centered at $-0,5R/+0.5R$.
   \label{fig:OC_profiles}} 
\end{figure*}
